---
title: "ClassSupport: from prototypical list to S4 class"
author: "Vincent J. Carey, stvjc at channing.harvard.edu"
date: "`r format(Sys.time(), '%B %d, %Y')`"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{ClassSupport: from prototypical list to S4 class}
  %\VignetteEncoding{UTF-8}
output:
  BiocStyle::html_document:
    highlight: pygments
    number_sections: yes
    theme: united
    toc: yes
---

# Purpose: reduce tedium of S4 class definition

Given a prototypical list of elementary R data
it is trivial but tedious to define a valid
S4 class with appropriate getter and setter methods.
DrS4's `ClassSupport` class helps with this.

# Example: Turtle

Stuart Lee's [blog post on S4](https://stuartlee.org/2019/07/09/s4-short-guide/) 
inspires the default
parameter settings in the `clgen` function.

```{r lkdef}
suppressPackageStartupMessages(library(DrS4))
args(clgen)
```

## Generate the basic definitions

Try it:
```{r ttt}
tt = clgen()
tt
```

We dump the code defining the class and its get/set methods.
```{r ddd}
dumpcs(tt)
```

To use the code, we can source it, or place in a
package.

```{r nnn}
tf = tempfile()
dumpcs(tt, tf)
source(tf)
tur = new("Turtle")
tur
path(tur)
path(tur) = matrix(c(1,1), nr=1)
tur
```
