---
title: "ClassSupport: from prototypical list to S4 class"
author: "Vincent J. Carey, stvjc at channing.harvard.edu"
date: "`r format(Sys.time(), '%B %d, %Y')`"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{ClassSupport: from prototypical list to S4 class}
  %\VignetteEncoding{UTF-8}
output:
  BiocStyle::html_document:
    highlight: pygments
    number_sections: yes
    theme: united
    toc: yes
---

# Purpose: reduce tedium of S4 class definition

Given a prototypical list of elementary R data
it is trivial but tedious to define a valid
S4 class with appropriate getter and setter methods.
DrS4's `ClassSupport` class helps with this.

# Example: Turtle

Stuart Lee's [blog post on S4](https://stuartlee.org/2019/07/09/s4-short-guide/) 
inspires the default
parameter settings in the `clgen` function.

```{r lkdef}
suppressPackageStartupMessages(library(DrS4))
args(clgen)
```

## Generate the basic definitions

Try it:
```{r ttt}
tt = clgen()
tt
```

Learn a little more about this infrastructure:
```{r lkckllk}
getClass(class(tt))
```

We dump the code defining the class and its get/set methods.
```{r ddd}
dumpcs(tt)
```

To use the code, we can source it, or place in a
package.

```{r nnn}
tf = tempfile()
dumpcs(tt, tf)
source(tf)
tur = new("Turtle")
tur
path(tur)
path(tur) = matrix(c(1,1), nr=1)
tur
```
## Extend the class

Stuart showed how a more functional turtle can be
defined -- one that holds a pen. We'll need a new
definition and new
getters and setters.

We defined a method
on our `ClassSupport` class to
produce the new class.

```{r doext}
newprops = list(colour = "pink", thickness = 1, on = FALSE)
nn = extendClassSupport(tt, newprops, "TurtleWithPen")
nn
dumpcs(nn)
```

We can now source that code to allow composition
of methods for TurtleWithPen.

# Envoi

There is something unsavory about this approach to
code generation.  I produced it in the face of a task
involving a configuration object that seems to require
many slots.  I wanted to avoid the temptation to
use simple functions and the at sign.  My hope is that
programs along the lines of those demonstrated here
will help lower the barrier to adoption of formal
class and method definitions in R programming.  There
are surely many improvements to be made in what has
been proposed here.



