---
title: "DrS4: help in contemplating S4 class usage"
author: "Vincent J. Carey, stvjc at channing.harvard.edu"
date: "`r format(Sys.time(), '%B %d, %Y')`"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{DrS4: help in contemplating S4 class usage}
  %\VignetteEncoding{UTF-8}
output:
  BiocStyle::html_document:
    highlight: pygments
    number_sections: yes
    theme: united
    toc: yes
---

# Observation: `methods` may report more than we need

We are interested in the SingleCellExperiment class.

It is defined in a package.

```{r dosce}
suppressPackageStartupMessages({
 library(SingleCellExperiment)
 library(DrS4)
 library(dplyr)
})
methods(class="SingleCellExperiment")
```

There are many methods listed, including '=='.

```{r chk1}
try(getMethod("==", "SingleCellExperiment"))
```

We can find the signatures for which '==' is
defined:
```{r lksm}
showMethods("==")
```

# Finding methods defined in a package

DrS4 aims to provide clearer access to the
methods actually defined for a class.  This requires
specifying a package where we look for the class
and its methods.  More work needs to be done in this domain.
Specifically, the function 'defdMethods' currently only
retrieves one method/signature for each generic method
defined for the class.

## Example

```{r useDrS4}
library(DrS4)
require("SingleCellExperiment")
scem = defdMethods(cl="SingleCellExperiment",
          pkg="SingleCellExperiment")
head(scem)
```

## Listing available coercion methods

Here we'll list methods
of coercing between classes involving SummarizedExperiment,
RangedSummarizedExperiment, and SingleCellExperiment.
```{r doex}
require("SummarizedExperiment")
se = defdMethods("SummarizedExperiment") # pkg has simple default
rse = defdMethods("RangedSummarizedExperiment", pkg="SummarizedExperiment")
cmb = try(rbind(scem,se,rse))
tmp = (cmb |> filter(method=="coerce"))
sl = (tmp |> select(sigs))[[1]]
names(sl) = tmp$cl
sl
```

