---
title: "DrS4: help in contemplating S4 class usage"
author: "Vincent J. Carey, stvjc at channing.harvard.edu"
date: "`r format(Sys.time(), '%B %d, %Y')`"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{}
  %\VignetteEncoding{UTF-8}
output:
  BiocStyle::html_document:
    highlight: pygments
    number_sections: yes
    theme: united
    toc: yes
---

# Observation

We are interested in the SingleCellExperiment class.

It is defined in a package.

```{r dosce}
suppressPackageStartupMessages({
 library(SingleCellExperiment)
 library(DrS4)
 library(dplyr)
 library(magrittr)
})
methods(class="SingleCellExperiment")
```

There are many methods listed, including '=='.

```{r chk1}
try(getMethod("==", "SingleCellExperiment"))
```

We can find the signatures for which '==' is
defined:
```{r lksm}
showMethods("==")
```

DrS4 will, ultimately, provide clearer access to the
methods actually defined for a class.  This requires
specifying a package where we look for the class
and its methods.  More work needs to be done in this domain.
Specifically, the function 'defdMethods' currently only
retrieves one method/signature for each generic method
defined for the class.

```{r useDrS4}
library(DrS4)
require("SingleCellExperiment")
scem = defdMethods("SingleCellExperiment")
head(scem)
```

The example for `defdMethods` shows one way to work with
multiple related classes.  Specifically, we'll list methods
of coercing between classes involving SummarizedExperiment,
RangedSummarizedExperiment, and SingleCellExperiment.
```{r doex}
require("SummarizedExperiment")
se = defdMethods("SummarizedExperiment")
rse = defdMethods("RangedSummarizedExperiment", "package:SummarizedExperiment")
cmb = try(rbind(scem,se,rse))
require("dplyr")
require("magrittr")
tmp = (cmb %>% filter(method=="coerce"))
sl = (tmp %>% select(sigs))[[1]]
names(sl) = tmp$cl
sl
```

